### 2023-01-31 manuscript.tex
please give me xelatex.. [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/a9e59367a493c3366c2f044abed56115cd182b08.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/a9e59367a493c3366c2f044abed56115cd182b08/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4059405651

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/f600bf52e21065865fb4f3a0f1fb349145c9e9ce/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/f600bf52e21065865fb4f3a0f1fb349145c9e9ce}{stain/2022-fdo-paper@f600bf5}
on January 31, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/a9e59367a493c3366c2f044abed56115cd182b08/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/a9e59367a493c3366c2f044abed56115cd182b08}{stain/2022-fdo-paper@a9e5936}
on January 31, 2023.
